\sectionTitle{Experience}{}

\begin{experiences}

\researchexperience
    {Present}   {University of Washington | Allen School of CSE{\normalfont  ~ [\href{https://www.cs.washington.edu/}{\small{\websiteSymbol}}]
    }}{Seattle, WA}{}
    {Sep 2024} {\textit{PhD Student | Advisor:  \href{https://homes.cs.washington.edu/~althoff/}{Prof. Tim Althoff}}\\
     Research on psychological safety in human-AI interaction and user modeling in the \href{https://bdata.uw.edu/}{BData group}.
    }
    \emptySeparator

\researchexperience
    {Jul 2024}   {Microsoft Research India{\normalfont  ~ [\href{https://www.microsoft.com/en-us/research/lab/microsoft-research-india/}{\small{\websiteSymbol}}]
    }}{Bangalore, India}{Bangalore, India}
    {Jul 2022} {\textit{Research Fellow | Advisor:  \href{https://www.microsoft.com/en-us/research/people/visesha/}{Dr. Vivek Seshadri}}\\
     Designed methods to enable knowledge acquisition and skilling through data annotation for low-income data annotators in rural and semi-urban India.
    }
    \emptySeparator

\researchexperience
    {2023}   {Cornell Tech | Social Technologies Lab{\normalfont  ~ [\href{https://s.tech.cornell.edu/}{\small{\websiteSymbol}}]
    }}{Remote}{}
    {2021} {\textit{Visiting Researcher | Advisors:  \href{https://tech.cornell.edu/people/mor-naaman/}{Prof. Mor Naaman}, \href{https://csslab.net/}{Prof. Maurice Jakesch}}\\
    Examined if and how writing assistants powered by biased language models can influence the opinion formation process and opinions of writers.
    }
    \emptySeparator
\researchexperience
    {Jul 2022}   {Indian Institute of Technology Bombay | Interaction Design for Indian Needs Lab{\normalfont  ~ [\href{http://idid.in/}{\small{\websiteSymbol}}]
    }}{Mumbai, India}{}
    {Aug 2021} {\textit{Research Associate | Advisor: \href{http://www.idc.iitb.ac.in/~anirudha/}{Prof. Anirudha Joshi}}\\
    Conducted user studies to understand mobile banking usage in low-literate and elderly users along with designing and testing a mobile banking application with interactive voice guidance.
    }
  \emptySeparator
\researchexperience
    {Jul 2022 }   {Ooloi Labs{\normalfont  ~ [\href{https://www.ooloilabs.in/}{\small{\websiteSymbol}}]
    }}{Remote}{}
    {Nov 2021} {\textit{Creative Technologist | Mentors: \href{http://akshayroongta.in/home/}{Akshay Roongta}, \href{https://www.linkedin.com/in/abrar-burk-083a1634/}{Abrar Burk}}\\
   Designed and developed data collection technologies such as interactive voice response systems for reporting human rights violations in Delhi slums and chatbots for grassroots monitoring of water quality.
    }
  \emptySeparator
\researchexperience
    {Jul 2019}   {Microsoft | India Development Center{\normalfont  ~ [\href{https://www.microsoft.com/en-in/msidc/}{\small{\websiteSymbol}}]
    }}{Bangalore, India}{}
    {May 2019} {\textit{User Experience Intern}\\
    Designed an intelligent user interface for an enterprise product for identifying and mitigating ad fraud on Bing Ads.
    }

\end{experiences}
% \vspace{-4mm}
