\sectionTitle{Select Design and Software Projects}{}

\begin{projects}

\projectb
	{Data collection tools for on-field reporting.}{Nov'21 - Jul'22}{}
	{\begin{itemize}
	\setlength\itemsep{0.3em}
     \item Used participatory design methods to design an interactive voice response system for low-literate women to report human rights violations in Delhi slums and a WhatsApp-based chatbot for water quality monitoring for on-ground volunteers.
     \item Developed the IVR system using the \href{https://developer.exotel.com/}{Exotel API} and a WhatsApp-based chatbot using \href{https://github.com/glific}{Glific}.
     \item Implemented APIs and database integrations for the IVR system and WhatsApp chatbot.
     \end{itemize}}

\projectb
	{Banking application with interactive voice guidance for low-literate and elderly users.}{Aug'21 - Jul'22}{}
		{\begin{itemize}
		\setlength\itemsep{0.3em}
     \item Designed an end-to-end banking application interface, user experience and interactions.
     \item Employed methods such as card sorting and heuristic evaluation for application design, evaluation and iteration.
     \item Used task-based usability testing for evaluating the design with low-literate and elderly users.
     \end{itemize}}

\projectb
    {Bing Fraud Linkage Analyser}{May'19 - Jul'19}{}
		{\begin{itemize}
		\setlength\itemsep{0.3em}
     \item Worked with a team of developers and researchers to build a ‘Search Fraud detection interface’ for the Bing search engine.
    \item Designed a novel intelligent interface that leverages clustering to identify potentially fraudulent ads in the search engine and help human reviewers catch fraudsters faster and more accurately.
     \end{itemize}}

\end{projects}
\vspace{-3mm}
